---
title: "Shiny (Question 4)"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
library(scales)
library(plyr)
library(magrittr)
library(stringr)
library(kableExtra)
library(rlist)
library(zoo) #index
library(data.table) # fread
library(PCIT)
library(psychometric)
```

```{r}
#install.packages("knitr")
#install.packages("scales")
#install.packages("plyr")
#install.packages("rlist")
#install.packages("zoo")
#install.packages("PCIT")
#install.packages("kableExtra")
#install.packages("DT")
#install.packages("ggplot2")
```

First we read in the data.  We add a date column that is in the "school year" format (ie. '2017-2018'). 
- This chunk attempts to remove duplicates by removing any duplicate record of a student ID taking the same test more than once in a year.
- The data set is large, so we make smaller copies to work with that do not hold all of the variables.  
```{r, include=FALSE}
# Read in csv:
file_list <- list.files(path = "~/TestAnalysisShiny/data/alldata",  pattern = "*.csv")
if(length(file_list) > 1){
 df_list <- lapply(file_list, fread, stringsAsFactors = FALSE, data.table = FALSE )
 data <- rbind.fill(df_list)
}else{
 data <- fread(path.expand(paste("~/TestAnalysisShiny/data/alldata/", list.files(path =   "~/TestAnalysisShiny/data/alldata",  pattern = "*.csv"), sep = "")), stringsAsFactors = FALSE, data.table = FALSE)
}

#This removes the record of the same student taking the same test in one year
data$TEST_DATE <- as.Date.factor(data$TEST_DATE)
data <- data[order(data$TEST_DATE),]
data <- data[!duplicated(data[c("TEST_ID","PERSON_ID")]),]

# This keeps only certain columns that we want to work with
#ourdata <- data[, c(3:6, 8:9, 21, 25:78)]
ourdata <- data[, c(3, 5, 8:9, 21, 25:78)]

# This creates a column for the year, in the format: "2017-2018"
ourdata$Month <- as.numeric(str_sub(string = ourdata$TEST_DATE, start = 6, end = 7))
ourdata$Year <-as.numeric(str_sub(string= ourdata$TEST_DATE, start=0, end=4))
school_year <- function(t) {
    ifelse(t < 8, (paste((ourdata$Year-1), ourdata$Year, sep = "-")), (paste(ourdata$Year, (ourdata$Year +1), sep = "-")))
  }
ourdata$SCHOOL_YEAR <- school_year(ourdata$Month)
#ba_Data <- ourdata[which(ourdata$TEST_ID %in% c(11:18)), c(1, 3:4, 7, 64, 8:61)]
#ourdata <- ourdata[, c(3, 5, 1, 7, 6, 2, 62:64)]
ba_Data <- ourdata[which(ourdata$TEST_ID %in% c(11:18)), c(1:5, 62, 6:32)]
ourdata <- ourdata[, c(1:5, 62, 6:59)]
```



THIS SECTION IS FOR ALL ASSESSMENTS OTHER THAN BELIEF AND APPLY

The next several chunks don't deal with "Belief and Apply" exams.  We'll deal with those later.
For now, this reads in the keys for all of the other exams.  They should be in the same folder ("TestAnalysisShiny/data")
  and should be named by Test ID (ie. "2.csv").
```{r}
# This reads in all the csv files in the current directory, which must be entered in the first chunk, line 9 ^ ^
setwd("~/TestAnalysisShiny/data")
file_list <- list.files(path = "~/TestAnalysisShiny/data",  pattern = "*.csv")

# Read in the answer keys only pertaining to the tests for which we have student data
#t <- aggregate(SCORE ~ TEST_ID, data = data, FUN = NROW)
t <- aggregate(SCORE ~ TEST_ID, data = ourdata, FUN = NROW)
#tests_taken <- t$TEST_ID
tests_taken <- t$TEST_ID %>% 
  as.numeric() %>%
  sort()
keep <- which(as.numeric(sub('\\..*', '', file_list)) %in% tests_taken)
df_list <- lapply(file_list[keep], fread, stringsAsFactors = FALSE, data.table = FALSE )
```


```{r}
# All csv files must be named "*testID*.csv", respectively.  This then pulls the testID's
names(df_list) <- as.numeric(sub('\\..*', '', file_list[keep]))

# This makes a list of the Test IDs, and the number of tests for each; making a matrix of test indices which functions can be applied over
test_Ids <- as.numeric(names(df_list))
num_Tests <- length(test_Ids)
test_lindex <- c(1:num_Tests)
test_index <- as.matrix(test_lindex)

# This makes a list of lists, each containing the keys for a test
list_ansrKeys <- function(x){
  ans_key <- x[!duplicated(x["Code"]),]
  ans_key[(ans_key$ItemType == "MC"), "CorrectOption"]
}

keys <- llply(df_list, list_ansrKeys)

# This function makes a list of 76 dfs, which each contain student responses
fx_extractResp <- function(x){
  ID <- test_Ids[x]
  len <- length(keys[[x]])
  stud_ans <- ourdata[ourdata$TEST_ID == ID, c(7:(6 + len))]
  #stud_ans <- data[data$TEST_ID == ID, c(25:(24 + len))]
  if(NROW(stud_ans == 1)){
    stud_ans[2,] <- stud_ans[1,]
  }
  stud_ans
}

stud_responses <- apply(test_index, MARGIN = 1, fx_extractResp)
# This takes the responses, cuts the number that was chosen, and gets rid of NA's
# It also gets rid of tests who have 25% or more NA
cut_num <- function(x){
  if(is.na(x) == TRUE){
    x <- 0
  }else if(x == ''){
    x <- 9
  }else(
  x <- as.numeric(str_sub(string = x, start = 2, end = 2 ))
  )
  
  if(x>3){
    x <- 8
  }else(x <- x)
}

nested_func <- function(x){
    stud_ans <- as.data.frame(apply(x, MARGIN = c(1,2), FUN = cut_num))
    stud_ans <- stud_ans[rowSums(is.na(stud_ans)) < (ncol(x)/4),]
    stud_ans[is.na(stud_ans)] <- 0
    stud_ans
}

stud_answers <- lapply(stud_responses, nested_func)

# This compares the responses to the answer keys
fx_grader <- function(x){
  df<- data.frame(stud_answers[[x]]) 
  t_key <- keys[[x]]
  t(apply(df, 1, function(x) x == t_key))
}

stud_tf <- apply(test_index, MARGIN = 1, fx_grader )

#  If needed, this gives a list of all the scores for the tests' MC
   test_scores <- laply(stud_tf, mean)


# This function makes a list of 76 df's, which each contain the Qtext, the correct Ans, and a column for each anstext
fx_analysis <- function(x){
  df <- x[!duplicated(x["Code"]),]
  df[(df$ItemType == "MC"), c("ItemText", "CorrectOption", "Option1", "Option2", "Option3")]
}

quest_analysis <- llply(df_list, fx_analysis)


fx_percent <- function(x){
  round(100*x, 2)
}

# This function creates a list of dataframes that contain information about how students repsonded to each question

fx_addstats <- function(x){
  tf <- stud_tf[[x]]
  ans <- stud_answers[[x]]
  n_Resp <- NROW(tf)
  
  ans_one <- apply(ans, MARGIN = c(1,2), function(y) y == 1 )
  ans_one <- as.data.frame(ans_one)
  one_Score <- colSums(ans_one)
  
  ans_two <- apply(ans, MARGIN = c(1,2), function(y) y == 2 )
  ans_two <- as.data.frame(ans_two)
  two_Score <- colSums(ans_two)
  
  ans_three <- apply(ans, MARGIN = c(1,2), function(y) y == 3 )
  ans_three <- as.data.frame(ans_three)
  three_Score <- colSums(ans_three)
  
  q_Num <- 1:NCOL(ans)
  q_Score <- fx_percent(colMeans(tf))
  
  
  df <- cbind(q_Num, one_Score, two_Score, three_Score, q_Score)
  df <- as.data.frame(df)
}
quest_Dfs <- llply(test_index, fx_addstats)
  # Now what we need to do is take our quest_Dfs and combine them with our quest_analysis Df's

fx_combine <- function(x){
  comb <- cbind(quest_analysis[[x]], quest_Dfs[[x]]) 
  ID <- rep(test_Ids[x], NROW(comb))
  comb$TestID <- as.numeric(ID)
  as.data.frame(comb)
}
merged_Dfs <- llply(test_index, fx_combine)
```

```{r}
df_Merged <- rbind.fill(merged_Dfs)

fx_Distractor <- function(x){
  op <- as.numeric(x[2])
  ans_Text <- x[(op + 2)]
  if(op == 1){
    num_Cor <- x[7]
    d_score1 <- x[8]
    d1 <- x[4]
    d_score2 <- x[9]
    d2 <- x[5]
  }else if(op == 2){
    num_Cor <- x[8]
    d_score1 <- x[7]
    d1 <- x[3]
    d_score2 <- x[9]
    d2 <- x[5]
  }else {
    num_Cor <- x[9]
    d_score1 <- x[7]
    d1 <- x[3]
    d_score2 <- x[8]
    d2 <- x[4]
    }
  
  if(d_score1 > d_score2){
    cbind(x[11], x[6], x[10], x[1], ans_Text, num_Cor, d1, d_score1, d2, d_score2)
  }else{
    cbind(x[11], x[6], x[10], x[1], ans_Text, num_Cor, d2, d_score2, d1, d_score1)
  }
}

df_Combined <- apply(df_Merged, MARGIN = 1, FUN = fx_Distractor)
df_Combined <- as.data.frame(t(df_Combined))
colnames(df_Combined) <- c("TEST_ID", "Q #", "Score", "Text", "Answer", "#", "Distractor 1", "#1", "Distractor 2", "#2")
df_Combined$TEST_ID <- as.numeric(as.character(df_Combined$TEST_ID))

for(i in 1:3){
  x <- (i*2) + 4
  y <- 10 + i
df_Combined[, x] <- as.numeric(as.character(df_Combined[, x]))
}

df_Combined$Score1 <- round(df_Combined[, 8] / (df_Combined[, 6] + df_Combined[, 8] + df_Combined[, 10]), 2)
df_Combined$Score2 <- round(df_Combined[, 10] / (df_Combined[, 6] + df_Combined[, 8] + df_Combined[, 10]), 2)
df_Combined$NResp <- df_Combined[, 6] + df_Combined[, 8] + df_Combined[, 10]
```

```{r}
fx_TestType <- function(x){
    TYPE <- numeric(length = (NROW(x)))
    x$TEST_ID <- as.numeric(x$TEST_ID)
    for (i in 1:NROW(x)) {
          ID <- x$TEST_ID[i]
          if(ID < 9 ){
               TYPE[i] <- "Learning Assessment"
            }else if (ID < 19 & ID > 10 ) {
              TYPE[i] <- "Belief And Apply" 
            }else if (ID == 100|ID == 200 | ID == 1101 | ID == 2201){
              TYPE[i] <- "Doctrinal Topics"
            }else if (ID > 100 & ID < 133 | ID >700 & ID < 736){
              TYPE[i] <- "Weekly Review"
            }else if (ID == 500 | ID == 600 | ID == 700 | ID == 800 | ID == 22 ){
              TYPE[i] <- "Pre-Assessments"
            }
            else {
              TYPE[i] <- "Other"
            }
    }
    cbind(x, TYPE)
}

df_Combined <-  fx_TestType(df_Combined)
ourdata2 <- fx_TestType(ourdata)
```


EVERYTHING ABOVE HERE DEALS WITH THE LEARNING ASSESSMENTS THAT AREN'T BELIEF AND APPLY

EVERYTHING BELOW HERE IS THE BELIEF AND APPLY ASSESSMENT PORTION


```{r}
# This chunk will create a report for the most missed questions for Learning Assessments 
# This reads in all the csv files in the current directory, which must be entered in the first chunk, line 9 ^ ^
setwd("~/TestAnalysisShiny/data/beliefapply")
BAfile_list <- list.files(path = "~/TestAnalysisShiny/data/beliefapply",  pattern = "*.csv")

# Read in the answer keys only pertaining to the tests for which we have student data
t <- aggregate(SCORE ~ TEST_ID, data = data, FUN = NROW)
tests_taken <- t$TEST_ID
tests_taken <- tests_taken[as.numeric(tests_taken) > 10 & as.numeric(tests_taken) < 19]
keep <- which(as.numeric(sub('\\..*', '', BAfile_list)) %in% tests_taken)
BAdf_list <- lapply(BAfile_list[keep], fread, stringsAsFactors = FALSE, data.table = FALSE )
# All csv files must be named "*testID*.csv", respectively.  This then pulls the testID's
names(BAdf_list) <- as.numeric(sub('\\..*', '', BAfile_list[keep]))
# Make a list of the Test IDs, and the number of tests for each; make a matrix of test indices which functions can be applied over
ba_Ids <- as.numeric(names(BAdf_list))
num_Tests <- length(ba_Ids)
test_lindex <- c(1:num_Tests)
ba_Index <- as.matrix(test_lindex)

# This makes a list of lists, each containing the doctrines for a test
fx_Doctrines <- function(x){
  keep_Cols <- which((str_sub(string = colnames(x), start = 1, end = 3 )) == "Row")
  l <- as.data.frame(t(x[c(1:2), keep_Cols]))
  n_Bel <- sum(l[, 1] != "")
  n_App <- sum(l[, 2] != "")
 
  df <- data.frame(Doctrine = unlist(l))
  df <- df[df != "",]
  doc <- data.frame(df, c(rep("Belief", n_Bel), rep("Apply", n_App)))
}

ba_Doctrines <- llply(BAdf_list, fx_Doctrines)

# This function makes a list of 76 dfs, which each contain student responses
fx_extractResp <- function(x){
  ID <- ba_Ids[x]
  len <- NROW(ba_Doctrines[[x]])
  stud_ans <- ourdata[ourdata$TEST_ID == ID, c(7:(6 + len))]
  #stud_ans <- data[data$TEST_ID == ID, c(25:(24 + len))]
  if(NROW(stud_ans) == 1){
    stud_ans[2,] <- stud_ans[1,]
  }
  stud_ans
}

ba_Responses <- apply(ba_Index , MARGIN = 1, fx_extractResp)
```


```{r}
# This chunk results in one list of "Belief" Data Frames, and one list of "Apply" Data Frames, one of each for each test
# Each Data frame contains all of the student's responses pertaining to each doctrine for that test

# We need to make sure that these symbols aren't deleted as we close and open RStudio- sometimes I come back and one of the symbols is just gone

#str_extract_all(x, regex(pattern = "\\?....", dotall = TRUE, ignore_case = TRUE))

#"I this is true.§(D)know||How much do you care about this doctrine?§(H)It is very important to me."

#my_Pattern <- "§..."
my_Pattern <- "§..."

# These functions make a list of the A-D answers
fx_Abcd <- function(x){
  
    if(is.na(x) == TRUE){
      x <- "NA"
    }else if(x == ''){
      x <- "EMPTY"
    }else{
      
      #ba_String <- str_extract_all(x, my_Pattern)
      ba_String <- str_extract_all(x, "\\(." )
      resp <- str_sub(string = ba_String[[1]], start = 2, end = 2)
      
      if(resp[1] > "D"){
        if(length(resp) > 1 && resp[2] < "E"){
          x <- resp[2]
        }else{x <- "ERROR"}  # For "Important", this means that it only has an E-H (or two?)
      }else{x <- resp[1]}
    }
}

fx_FirstBa <- function(x){
  as.data.frame(apply(x, MARGIN = c(1, 2), FUN = fx_Abcd))
}         

# These functions make dataframes of all of the E-H answers
fx_Efgh <- function(x){
  
    if(is.na(x) == TRUE){
      x <- "NA"
    }else if(x == ''){
      x <- "EMPTY"
    }else{
      #ba_String <- str_extract_all(x, my_Pattern)
      ba_String <- str_extract_all(x, "\\(." )
      resp <- str_sub(string = ba_String[[1]], start = 2, end = 2)
      
      if(resp[1] < "E"){
        if(length(resp) > 1 & resp[2] > "D"){
          x <- resp[2]
        }else{x <- "ERROR"}  # For "Know", this means that it only has an A-D (or two?)
      }else{x <- resp[1]}
    }
}

fx_SecondBa <- function(x){
  as.data.frame(apply(x, MARGIN = c(1, 2), FUN = fx_Efgh))
}         


ba_Abcd <- lapply(ba_Responses, fx_FirstBa)
ba_Efgh <- lapply(ba_Responses, fx_SecondBa)
```

```{r}
fx_BaCombine <- function(x){
  
 df <- as.data.frame(ba_Doctrines[[x]])
 # add a list that will become the care column
 q_Split <- sum(df[, 2] == "Belief" )
 q_Num <- q_Split + sum(df[, 2] == "Apply")
 
 a_List <- colSums(ba_Abcd[[x]] == "A")
 b_List <- colSums(ba_Abcd[[x]] == "B")
 c_List <- colSums(ba_Abcd[[x]] == "C")
 d_List <- colSums(ba_Abcd[[x]] == "D")

 e_List <- colSums(ba_Efgh[[x]] == "E")
 f_List <- colSums(ba_Efgh[[x]] == "F")
 g_List <- colSums(ba_Efgh[[x]] == "G")
 h_List <- colSums(ba_Efgh[[x]] == "H")
 

 care_1 <- c(h_List[1:q_Split], d_List[(q_Split+1):q_Num])
 care_2 <- c(g_List[1:q_Split], c_List[(q_Split+1):q_Num])
 care_3 <- c(f_List[1:q_Split], b_List[(q_Split+1):q_Num])
 care_4 <- c(e_List[1:q_Split], a_List[(q_Split+1):q_Num])
 
 bel_1 <- c(d_List[1:q_Split], rep(1000, (q_Num - q_Split)))
 bel_2 <- c(c_List[1:q_Split], rep(1000, (q_Num - q_Split)))
 bel_3 <- c(b_List[1:q_Split], rep(1000, (q_Num - q_Split)))
 bel_4 <- c(a_List[1:q_Split], rep(1000, (q_Num - q_Split)))
 
 app_1 <- c(rep(1000, q_Split), h_List[(q_Split+1):q_Num])
 app_2 <- c(rep(1000, q_Split), g_List[(q_Split+1):q_Num])
 app_3 <- c(rep(1000, q_Split), f_List[(q_Split+1):q_Num])
 app_4 <- c(rep(1000, q_Split), e_List[(q_Split+1):q_Num]) 
 
 ID <- rep(ba_Ids[x], q_Num)
 
 colnames(df) <- c("Doctrine", "Type")
 y <- as.data.frame(cbind(ID, df, care_1, care_2, care_3, care_4, bel_1, bel_2, bel_3, bel_4, app_1, app_2, app_3, app_4))
 
 y$Care_Score <- ((y$care_1*4) + (y$care_2*3) + (y$care_3*2) + (y$care_4*1) ) / (y$care_1 + y$care_2 + y$care_3 + y$care_4)

 
 y$BA_score <- c(1:q_Num)
 
  for (i in 1:q_Num) {
    if(i < (q_Split +1)){
      
      y$BA_score[i] <- ((y$bel_1[i] *4) + (y$bel_2[i]*3) + (y$bel_3[i]*2) + (y$bel_4[i]*1) ) / (y$bel_1[i] + y$bel_2[i] + y$bel_3[i] + y$bel_4[i])
      
    }else{
      y$BA_score[i] <- ((y$app_1[i] *4) + (y$app_2[i]*3) + (y$app_3[i]*2) + (y$app_4[i]*1) ) / (y$app_1[i] + y$app_2[i] + y$app_3[i] + y$app_4[i])
    }
  }
 y
}
ba_Combined <- 0
ba_Combined <- apply(ba_Index , MARGIN = 1, fx_BaCombine)
```


```{r}
# This gives the "Scores" for each test
fx_BaScores <- function(x){
  ID <- ba_Ids[x]
  df <- ba_Combined[[x]]
  score_Care <- mean(df$Care_Score)
  score_Bel <- mean(df$BA_score[df$Type == "Belief"])
  score_App <- mean(df$BA_score[df$Type == "Apply"])
  as.data.frame(cbind(ID, score_Care, score_Bel, score_App))
}
ba_Scores <- apply(ba_Index , MARGIN = 1, fx_BaScores)
df_BaScore <- rbind.fill(ba_Scores)

```


```{r}
# Above we have a dataframe with just averages for each test, let's make dfs for each one comparing care to bel and app

fx_BelComb <- function(x){
  x$Num <- 1:NROW(x)
  x[x$Type == "Belief", c(1:11,  16:18)]
  
}
list_Belief <- llply(ba_Combined, fx_BelComb)

fx_AppComb <- function(x){
  x$Num <- 1:NROW(x)
  x[x$Type == "Apply", c(1:7, 12:18)]
}
list_Apply <- llply(ba_Combined, fx_AppComb)

df_CombBelief <- rbind.fill(list_Belief)
df_CombApply <- rbind.fill(list_Apply)

list_BaData <- list(df_BaScore, df_CombBelief, df_CombApply)

colnames(df_CombBelief)[8:11] <- c("BelApp_1", "BelApp_2", "BelApp_3", "BelApp_4")

colnames(df_CombApply)[8:11] <- c("BelApp_1", "BelApp_2", "BelApp_3", "BelApp_4")

df_BaMerged <- rbind.fill(df_CombApply, df_CombBelief)

```


```{r}
fx_BATest <- function(x){
    Name <- numeric(length = (NROW(x)))
    x$ID <- as.numeric(x$ID)
    for (i in 1:NROW(x)) {
          ID <- x$ID[i]
          if(ID == 11 ){
               Name[i] <- "Old Testament 1 (Gen-Ruth)"
            }else if (ID == 12 ) {
              Name[i] <- "Old Testament 2 (1Sam-Mal)" 
            }else if (ID == 13){
              Name[i] <- "New Testament 1 (Mat-John)"
            }else if (ID == 14){
              Name[i] <- "New Testament 2 (Acts-Rev)"
            }else if (ID == 15){
              Name[i] <- "BOM 1 (Nep-Alm)"
            }else if (ID == 16){
              Name[i] <- "BOM 2(Alm-Mor)"
            }else if (ID == 17){
              Name[i] <- "D&C 1 (1-75)"
            }else if (ID == 18){
              Name[i] <- "D&C 2"
            }else {
              Name[i] <- "Other"
            }
    }
    cbind(x, Name)
}

df_BALong <- fx_BATest(df_BaMerged)
```




```{r}
choices_df <-  data.frame(
names <-  c("All", "Old Testament 1 (Gen-Ruth)", "Old Testament 2 (1Sam-Mal)", "New Testament 1 (Mat-John)", "New Testament 2 (Acts-Rev)", "BOM 1 (Nep-Alm)", "BOM 2(Alm-Mor)", "D&C 1 (1-75)", "D&C 2"),
id <- 10:18)
colnames(choices_df) <- c("names", "ID")


df_Scatter <- data.frame(
  names <- c("Importance Level", "Belief Level", "Application Level"),
  id <- 1:3)
colnames(df_Scatter) <- c("names", "ID")
```



```{r}
  my_BAData <- df_BALong
  
  for(i in 1:NROW(my_BAData)){
    my_BAData$Num_care[i] <- sum(my_BAData[i, c(4:7)])
    my_BAData$Num_BelApp[i] <- sum(my_BAData[i, c(8:11)])
  }
  
  
  for(i in 1:NROW(df_BALong)){
    for(n in 1:8){
      n <- n + 3
      if(n < 8){
        my_BAData[i, n] <- round((my_BAData[i,n] / my_BAData$Num_care[i]), 2)
      }else{
        my_BAData[i, n] <- round((my_BAData[i, n] / my_BAData$Num_BelApp[i]), 2)
      }
    }
  }
  
  colnames(my_BAData)[4:7] <- c("Very Important", "Important", "Somewhat Important", "Not Important")
  
  my_BAData$BA_score <- round(my_BAData$BA_score , 2)
  my_BAData$Care_Score <- round(my_BAData$Care_Score, 2)
  
  my_AppData <- my_BAData[as.character(my_BAData$Type) == "Apply", c(15, 14, 2, 4:11) ]
  my_BelData <- my_BAData[as.character(my_BAData$Type) == "Belief", c(15, 14, 2, 4:11) ]
  
  colnames(my_AppData)[8:11] <- c("Always", "Almost Always", "Sometimes", "Rarely or Never")
  colnames(my_BelData)[8:11] <- c("Know", "Believe", "Sort of believe", "Don't know if")
```

###  EXPERIMENTAL Belief and Apply vvv 

```{r}
combAr <- subset(data, data$TEST_ID %in% ba_Ids)
areas <- as.matrix(unique(combAr$AREA))
areaInd <- as.matrix(1:length(areas))

fx_AreaBA <- function(x){
  
  area <<- areas[x]
  
  fx_extractResp <<- function(x){
    ID <- ba_Ids[x]
    len <- NROW(ba_Doctrines[[x]])
    stud_ans <- data[data$TEST_ID == ID, c(21, 25:(24 + len))]
    stud_ans <- stud_ans[stud_ans$AREA == area, 2:NCOL(stud_ans) ]
    if(NROW(stud_ans) == 1){
      stud_ans[2,] <- stud_ans[1,]
    }else if(NROW(stud_ans) == 0){
      stud_ans[1,] <- NA
      #stud_ans[1, 1] <- area
    }else{stud_ans <- stud_ans}
    stud_ans
  }

  ba_Responses <<- apply(ba_Index , MARGIN = 1, fx_extractResp)
  
  ba_Abcd <<- lapply(ba_Responses, fx_FirstBa)
  ba_Efgh <<- lapply(ba_Responses, fx_SecondBa)
  
  ba_Combined <<- 0
  ba_Combined <<- apply(ba_Index , MARGIN = 1, fx_BaCombine)
  
  
  
  list_Belief <<- llply(ba_Combined, fx_BelComb)
  list_Apply <<- llply(ba_Combined, fx_AppComb)
  
  df_CombBelief <<- rbind.fill(list_Belief)
  df_CombApply <<- rbind.fill(list_Apply)
  
  colnames(df_CombBelief)[8:11] <<- c("BelApp_1", "BelApp_2", "BelApp_3", "BelApp_4")

  colnames(df_CombApply)[8:11] <<- c("BelApp_1", "BelApp_2", "BelApp_3", "BelApp_4")

  df_BaMerged <<- rbind.fill(df_CombApply, df_CombBelief)
  
  df_BALong <<- fx_BATest(df_BaMerged)
  
  Area_BAData <<- df_BALong
  
  for(i in 1:NROW(Area_BAData)){
    Area_BAData$Num_care[i] <- sum(Area_BAData[i, c(4:7)])
    Area_BAData$Num_BelApp[i] <- sum(Area_BAData[i, c(8:11)])
  }
  
  
  for(i in 1:NROW(df_BALong)){
    for(n in 1:8){
      n <- n + 3
      if(n < 8){
        Area_BAData[i, n] <- round((Area_BAData[i,n] / Area_BAData$Num_care[i]), 2)
      }else{
        Area_BAData[i, n] <- round((Area_BAData[i, n] / Area_BAData$Num_BelApp[i]), 2)
      }
    }
  }
  
  colnames(Area_BAData)[4:7] <- c("Very Important", "Important", "Somewhat Important", "Not Important")
  
  Area_BAData$BA_score <- round(Area_BAData$BA_score , 2)
  Area_BAData$Care_Score <- round(Area_BAData$Care_Score, 2)
  
  my_AppData <- Area_BAData[as.character(Area_BAData$Type) == "Apply", c(15, 14, 2, 4:11) ]
  my_BelData <- Area_BAData[as.character(Area_BAData$Type) == "Belief", c(15, 14, 2, 4:11) ]
  
  colnames(my_AppData)[8:11] <- c("Always", "Almost Always", "Sometimes", "Rarely or Never")
  colnames(my_BelData)[8:11] <- c("Know", "Believe", "Sort of believe", "Don't know if")
  
  Area_BAData
  
  
}
#area_List <- apply(areaInd, MARGIN = 1, fx_AreaBA) <- this has some bugs, we can work this out if we need to 
#View(area_List[[1]])
#View(area_List[[2]])
```

```{r}
choices_df <-  data.frame(
names <-  c("All", "Old Testament 1 (Gen-Ruth)", "Old Testament 2 (1Sam-Mal)", "New Testament 1 (Mat-John)", "New Testament 2 (Acts-Rev)", "BOM 1 (Nep-Alm)", "BOM 2(Alm-Mor)", "D&C 1 (1-75)", "D&C 2"),
id <- 10:18)
colnames(choices_df) <- c("names", "ID")


df_Scatter <- data.frame(
  names <- c("Importance Level", "Belief Level", "Application Level"),
  id <- 1:3)
colnames(df_Scatter) <- c("names", "ID")


df_Area <- data.frame(
  names <- areas, 
  id <- areaInd
)
colnames(df_Area) <- c("names", "ID")

m <- as.numeric(str_sub(file_list[keep], 1, -5))
no_BA <- sort(as.numeric(str_sub(file_list[keep], 1, -5)))


m <- subset(test_Ids, !(test_Ids %in% c(11:18)))

no_BA <- data.frame(
  names <- sort(m), 
  id <- order(m)
)
colnames(no_BA) <- c("names", "ID")


```

